Deeply Virtual Compton Scattering measurement off bound protons

### 2018-10-15 eg6-letters/incoherent/2nd-adhocreview/2nd_adhoc_comments.tex
some cleaning
Modif on Incoherent for ad hoc

\title{Second round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)}

@@

The new plot of the data versus t shows far more clearly the point you are 
trying to make about possible modification of the struck proton in 4He. We are 
a bit concerned however that it would not be clear to the reader that there is 
significant expected smearing of the t variable due to the Fermi motion of the 
initial proton. The question we have is whether horizontal error bars on your 
plot, which would include the bin width effects and the smearing of the t 
variable, could be added to make this explicitly clear to the reader.\\
   \textcolor{blue}{Updated.}\\

>>>>

\title{Second round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop, Kevin Giovanetti, Zein-Eddine Meziani)}

@@

The new plot of the data versus t shows far more clearly the point you are 
trying to make about possible modification of the struck proton in 4He. We are 
a bit concerned however that it would not be clear to the reader that there is 
significant expected smearing of the t variable due to the Fermi motion of the 
initial proton. The question we have is whether horizontal error bars on your 
plot, which would include the bin width effects and the smearing of the t 
variable, could be added to make this explicitly clear to the reader.\\
   \textcolor{blue}{We used the kinematics of the photons to determine $t$ specifically
   in order to avoid such uncertainty linked to the initial proton kinematics (see 
   Appendix H of the analysis note for details). However, the paper was unclear on 
   the topic, we have changed Fig 1 and added a statement line 160-163 to clarify 
   this in the new version.}\\

### 2018-10-15 eg6-letters/incoherent/incoherent_prl.tex
Modif on Incoherent for ad hoc

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton, calculated 
from 4-momentum vectors of incoming and outgoing photons, was required to be 
greater than a minimum allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We used kinematics of the photons for determining the $t$ to 
avoid uncertainty of the initial proton kinematics due to Fermi motion. Then, 
the exclusivity of the incoherent DVCS events was ensured by imposing 
constraints on the kinematical variables resulting from conserving the 
four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton, calculated 
from 4-momentum vectors of incoming and outgoing photons, was required to be 
greater than a minimum allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.
